\documentclass[conference]{IEEEtran}
\input{preamble.tex}

\begin{document}

\title{Technical debt}

\author{
\IEEEauthorblockN{Yasutaka Kamei$^{\dag}$, Everton Maldonado$^{\dag\dag}$, Emad Shihab$^{\dag\dag}$, and Naoyasu Ubayashi$^{\dag}$}
\IEEEauthorblockA{
$^{\dag}$Principles of Software Languages Group (POSL), Kyushu University, Fukuoka, Japan\\
$^{\dag\dag}$Department of Computer Science and Software Engineering, Concordia University, Montr\'eal, Canada\\
Email: $^{\dag}$\{kamei, ubayashi\}@ait.kyushu-u.ac.jp, $^{\dag\dag}$\{e\_silvam, eshihab\}@encs.concordia.ca
}
}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
abstract.
\end{abstract}

\IEEEpeerreviewmaketitle

% Here is Yasu't note
\begin{comment}

\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{introduction.tex}
\section{Introduction}
\para{What is technical debt?}

\para{Describe more detail of technical debt and current problem in the domain}

\para{The goal and approach of this study}

\para{Dataset}

\para{Contributions}

\cite{Potdar2014ICSME}
\cite{Maldonado2015MTD}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{background.tex}
\section{Related Work}
\para{Technical debt}

\cite{Guo2011ICSM}:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Case Study Setup}
The goal of this study is \todo{purpose.}.
...

We formalize our study in the following research questions:

\todo{List up research question}

To conduct our case study, we use data from ...

\subsection{Project Data Extraction}

\subsection{Interest}
To measure interest, we use source code metrics. We use Understand, which is a well-known tool, to measure source code metrics. 

\para{how to calculate metrics?}

In this study, we consider the relative size of ... as interest. For example, 

\para{how to identify when a technical debt are introduced and removed?}
From that version, we obtain patches between two versions over all versions for each file that includes technical debt. Then, we check each patch about whether or not technical debt is introduced/removed. Some of them are not removed. If so, we use latest commits. We calculate the difference of a metric between two versions when technical debt is introduced and removed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{RQ1: Can we quantify interest of technical debt at the function-level?}
\smallsection{Motivation}
\todo{need to read some papers that say technical debt is bad. So we want to quantify it.}

\smallsection{Approach}
\para{We calculate the interest.}

\smallsection{Results}

Figure xx shows that the distribution of interest. X

\para{Put the distribution of interest?}

\conclusionbox{Result of RQ1: 22\%-36\% of technical debt has positive interest.}

\subsection{RQ2: Does the interest differ based on the type of technical debt?}
\smallsection{Motivation}
There are several type of technical debt such as defect technical debt and design technical debt. 
To better understand the interest, we would like to analayze ...

\smallsection{Approach}
We classify technical debt into categories and calculate interest in each category.

\smallsection{Results}
Table X shows the number and the percentage of technical debt 

\conclusionbox{Result of RQ2}

\subsection{RQ3: manual analysis}
\smallsection{Motivation}

\smallsection{Approach}

\smallsection{Results}

\conclusionbox{Result of RQ3}

\section{Discussion}
\para{Put additional analysis when considering time period.}

\para{Put additional analysis when considering other metrics.}

\para{Put the analysis for showing the method that includes more than one technical debt in one version.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Threat to Validity}

\smallsection{Construct Validity}

\smallsection{Internal Validity}
\para{Technical debt is classified by one person.}

\smallsection{External Validity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%\input{conclusion.tex}
\para{Summary of this work.}

\section*{Acknowledgment}
This research was partially supported by JSPS KAKENHI Grant Numbers 15H05306.

\bibliographystyle{abbrv}
%\bibliographystyle{IEEEtranN}
\bibliography{reference}


\end{document}

