---
title: 'RQ1: Can we quantify interest of TD at the functional level? How much is the
  interest? (Version 5)'
author: "Yasutaka Kamei"
date: "Feb 13th, 2016"
output: pdf_document
---

# What's new in the version 5?
- Add histgrams

# What's new in the version 4?
- We used the new dataset that solves one bug that is fixed by Everton.

# Data Load
```{r}
setwd("/Users/kamei/Research/techdebt/msr16_td_interest/")
source("./r_scripts/data_read.r")
```

# Data Summary
- (Step 1) choose one of duplicated method and version name
- (Step 2) only use technical debt including metrics
```{r}
nrow(data)
apply(data.s1[,c("version_name","CountInput_v1","CountInput_v2")], 2, function(x){sum(x == -1) })
```

### Observation
- The number of methods that cannot be linked between Evernton's data and metrics data
    - 171 => 221 (introducing) 
    - 101 => 94 (being found as last version)

# (Step 3) use technical debt including non 0 for division
## CountLine
```{r}
summary(data.CountLine.all$Project)
summary(data.CountLine.positive$Project)
summary(data.CountLine.negative$Project)

summary(data.CountLine.positive$Project) / summary(data.CountLine.all$Project) * 100
summary(data.CountLine.negative$Project) / summary(data.CountLine.all$Project) * 100
```

## CountInput
```{r}
summary(data.CountInput.all$Project)
summary(data.CountInput.positive$Project)
summary(data.CountInput.negative$Project)

summary(data.CountInput.positive$Project) / summary(data.CountInput.all$Project) * 100
summary(data.CountInput.negative$Project) / summary(data.CountInput.all$Project) * 100
```

### Observation
- The number of all methods is 837
    - (s1) 754
    - (s2) 488
- We use 71, 181, and 236 methods including technical debt. 
    - The data set we used had 67 (ant), 169(jmeter) and 268(jruby) technical debt.
- 32.6%-44.2% of technical debt has positive interest.
- 13.8%-28.7% of technical debt has negative interest.

## CountLine
```{r}
# interest of CountLine (LOC)
fc <- factor(data.CountLine.all$Project)
interest <- data.CountLine.all$interest
tapply(interest, fc, summary)

fc <- factor(data.CountLine.positive$Project)
interest <- data.CountLine.positive$interest
tapply(interest, fc, summary)



fc <- factor(data.CountLine.negative$Project)
interest <- data.CountLine.negative$interest
tapply(interest, fc, summary)
```

## CountInput
```{r}
# CountInput
fc <- factor(data.CountInput.all$Project)
interest <- data.CountInput.all$interest
tapply(interest, fc, summary)

fc <- factor(data.CountInput.positive$Project)
interest <- data.CountInput.positive$interest
tapply(interest, fc, summary)

fc <- factor(data.CountInput.negative$Project)
interest <- data.CountInput.negative$interest
tapply(interest, fc, summary)
```


# Plot
```{r}
library(reshape2)
library(ggplot2)

if(0){
idx <- data.CountLine.positive$Project == "apache-ant"
a1 <- data.frame(Interest=data.CountLine.positive[idx,"interest"]) 
g = ggplot(a1, aes(x=Interest, y=..density.., fill=T), lims(x = c(0,400)))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-ant.pdf", plot = g, width = 8.09, height = 5)

idx <- data.CountLine.positive$Project == "apache-jmeter"
a2 <- data.frame(Interest=data.CountLine.positive[idx,"interest"]) 
g = ggplot(a2, aes(x=Interest, y=..density.., fill=T, lims(x = c(0,400))))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-jmeter.pdf", plot = g, width = 8.09, height = 5)

idx <- data.CountLine.positive$Project == "jruby"
a3 <- data.frame(Interest=data.CountLine.positive[idx,"interest"]) 
g = ggplot(a3, aes(x=Interest, y=..density.., fill=T), lims(x = c(0,400)))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-jruby.pdf", plot = g, width = 8.09, height = 5)
}

if(0){
idx <- data.CountInput.all$Project == "apache-ant"
a1 <- data.frame(Interest=data.CountInput.all[idx,"interest"]) 
g = ggplot(a1, aes(x=Interest, y=..density.., fill=T), lims(x = c(0,400)))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-ant-fanin.pdf", plot = g, width = 8.09, height = 5)

idx <- data.CountInput.all$Project == "apache-jmeter"
a2 <- data.frame(Interest=data.CountInput.all[idx,"interest"]) 
g = ggplot(a2, aes(x=Interest, y=..density.., fill=T, lims(x = c(0,400))))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-jmeter-fanin.pdf", plot = g, width = 8.09, height = 5)

idx <- data.CountInput.all$Project == "jruby"
a3 <- data.frame(Interest=data.CountInput.all[idx,"interest"]) 
g = ggplot(a3, aes(x=Interest, y=..density.., fill=T), lims(x = c(0,400)))
g = g + geom_density(alpha = 0.5) + xlim(0, 400) + ylim(0,0.04) + guides(fill=FALSE)
print(g)
ggsave(file = "./tex/figures/rq1-jruby-fanin.pdf", plot = g, width = 8.09, height = 5)
}
```