---
title: 'RQ1: Can we quantify interest of TD at the functional level? How much is the
  interest? (Version 2)'
author: "Yasutaka Kamei"
date: "Feb 11th, 2016"
output: pdf_document
---

# What did we revise?
- We divide one whole dataset into three projects (jruby, Ant and jmeter)
- To calcuate interest, we use the ratio of metrics value of v2 in it of v1. The positive value means we may need to spend additional cost.
    - For division, we exclude the technical debt that has 0 in v1. We show the number of the excluded technical debt.
    - Previous report measured the interest by substracting the metric value of v2 - the metric value v1.
- We use only one of duplicate technical debt that has same function name and same introducing version

# Data Overview
```{r}
data <- read.csv("/Users/kamei/Research/techdebt/msr16_td_interest/datasets/CSV/technical_debt_summary.csvinterest.ssv", sep="#")
fc <- factor(data$Project)

# the number of technical debt at the method-level
tapply(data$Project, fc, length)

# choose one of duplicated method and version name
method_and_version_name <- paste(data$Method_Signature, data$v1, sep="")
sum(duplicated(method_and_version_name))
data <- data[!duplicated(method_and_version_name), ] 
fc <- factor(data$Project)
tapply(data$Project, fc, length)

# any correlation?
cor(data[,c("CountInput_v1","CountOutput_v1","CountLine_v1","Cyclomatic_v1","MaxNesting_v1")],method="spearman")
cor(data[,c("CountInput_v2","CountOutput_v2","CountLine_v2","Cyclomatic_v2","MaxNesting_v2")],method="spearman")
```

### Observation
- 140 technical debt is removed due to duplication
- apache-ant has 84 technical debt. The number may be small.
- The following pairs have more than 0.8 correlation value
    - (CountOutput, CountLine), (CountOutput, Cyclomatic), (CountLine, Cyclomatic), (CountLine, MaxNesting), (Cyclomatic, MaxNesting)
    - So we report the results of fanin and countline.

# How many technical debt can we map between a metrics file and Everton's summary file?
*_v1 means the version that introduces technical debt and *_v2 means the last version that technical debt was found.

```{r}
# the number of technical debt that cannot be mapped between a metrics file
#and Everton's summary file
tapply(data$version_name, fc, function(x){sum(x == -1) })
tapply(data$CountInput_v1, fc, function(x){sum(x == -1) })
tapply(data$CountInput_v2, fc, function(x){sum(x == -1) })

# the number of technical debt that have metrics in both versions
# of introduction and last_found
a <- data[(data[, "CountInput_v1"] != -1 & data[, "CountInput_v2"] != -1), ]
fc.a <- factor(a$Project)
tapply(a$version_name, fc.a, length)
```

### Observation
- jruby misses 114 technical debt in v1 and 82 in v2.
- 67 (ant), 169(jmeter) and 268(jruby) technical debt has metrics in both versions of introduction and last_found.
- We need to discuss how to solve such missed technical debt.

# How much is the interest?
We target 67 (ant), 169(jmeter) and 268(jruby) technical debt in this analysis.
For each technical debt, we measure the ratio of metrics value of v2 in it of v1. We use 5 metrics as interest.

## CountInput (fanin)
```{r}
# interest of CountInput (fanin)
idx <- a[,"CountInput_v1"] == 0
sum(idx)
b <- a[!idx, ]
fc.b <- factor(b$Project)
interest <- (b[,"CountInput_v2"] ) / (b[,"CountInput_v1"])

# summary of interest for all technical debt
tapply(interest, fc.b, summary)

# the number of the percenage of positive interest, same interest, positive interest, negative interest
tapply(interest, fc.b, function(x){c( round((sum(x > 1)/ length(x) * 100)), sum(x==1), sum(x > 1), sum(x < 1)) } )

# summary of interest for only technical debt that has positive / negative value.
tapply(interest, fc.b, function(x){summary(subset(x, x !=1))} )


# interest of CountLine (LOC)
idx <- a[,"CountLine_v1"] == 0
sum(idx)
b <- a[!idx, ]
fc.b <- factor(b$Project)
interest <- (b[,"CountLine_v2"] ) / (b[,"CountLine_v1"])

# summary of interest for all technical debt
tapply(interest, fc.b, summary)

# the number of the percenage of positive interest, same interest, positive interest, negative interest
tapply(interest, fc.b, function(x){c( round((sum(x > 1)/ length(x) * 100)), sum(x==1), sum(x > 1), sum(x < 1)) } )

# summary of interest for only technical debt that has positive / negative value.
tapply(interest, fc.b, function(x){summary(subset(x, x !=1))} )
```

### Observation
- 22%-36% of technical debt has positive interest.
- If we focus on technical debt that has more than 1 interest
    - the number of technical debt that have positive interest is more than negative interest one

```{r}
# the top interest tech debt?
met_v1 <- "CountInput_v1"
met_v2 <- "CountInput_v2"

data.CountInput <- data[,c("Project", "Method_Signature", met_v1, met_v2)]
data.CountInput <- data.CountInput[(data.CountInput[, met_v1] != -1 & data.CountInput[, met_v2] != -1), ]
idx <- order(data.CountInput[,met_v2] - data.CountInput[,met_v1], decreasing = T)
head(data.CountInput[idx,])
```

### Observation
- [Discuss] if technical debt has same version and same method siguniture, should we remove one of them?
    - We soloved the above point.

# [Emad]  I think one thing to measure is the metric value in v-1/metric value in v-2. Of course we can only do this for non-zero differences.

```{r}
data.CountInput = subset(data.CountInput, data.CountInput$CountInput_v1 !=0)

library(vioplot)

idx.ant <- data.CountInput[,"Project"] == "apache-ant"
idx.jmeter <- data.CountInput[,"Project"] == "apache-jmeter"
idx.jruby <- data.CountInput[,"Project"] == "jruby"

ant <- data.CountInput[idx.ant,met_v2]/data.CountInput[idx.ant,met_v1]
jmeter <- data.CountInput[idx.jmeter,met_v2]/data.CountInput[idx.jmeter,met_v1]
jruby <- data.CountInput[idx.jruby,met_v2]/data.CountInput[idx.jruby,met_v1]

plot(0, 0, type = "n", xlab = "", ylab = "", axes = FALSE,
     xlim = c(0.5, 3.5), ylim = range(c(ant, jmeter, jruby)))

axis(side = 1, at = 1:3, labels = c("Ant", "Jmeter", "jruby"))
axis(side = 2)                                     

vioplot(ant, at = 1, col = "orange", add = TRUE)
vioplot(jmeter, at = 2, col = "seagreen", add = TRUE)
vioplot(jruby, at = 3, col = "blue", add = TRUE)

# How much percentage does technical debt has double interest?
sum(ant >= 2)
sum(jmeter >= 2)
sum(jruby >= 2)
```

### Observation
- There are several technical debt of which the ratio is more than 2. This means that the dependency of technical debt becomes double before being removed.

